A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-31 4_method.tex
change interpretation of b^-1 : now works on lower bead count

We call a distance $d$ `preferred' when $d = p(b(d))$
For our method we require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.

The following restrictions hold:
\begin{itemize}
\item $b(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0, t \geq 0$
\item $120\degree < \alpha_{\text{max}} \leq 180\degree$
\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $p$ is within the range of optimal: $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
%\item $b \left( p(n) \right) = n$ % follows from the above!
\item $b$ is monotonic: $ b(d) \leq b(d + \epsilon)$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\item $t$ is viable: $t(n) < \left( p(n + 1) - p(n) \right) /{2 \cos \alpha_\text{max}}$
\end{itemize}

>>>>

We call a distance $d$ `preferred' when $d = p(b(d))$
For our method we require the inverse $b^{-1}(n) := \argmax_d b(d) = n$.

The following restrictions hold:
\begin{itemize}
\item $b(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0, t \geq 0$
\item $120\degree < \alpha_{\text{max}} \leq 180\degree$
\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $p$ is within the range of optimal: $b^{-1}(n - 1) < p(n) < b^{-1}(n)$
%\item $b \left( p(n) \right) = n$ % follows from the above!
\item $b$ is monotonic: $ b(d) \leq b(d + \epsilon)$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\item $t$ is viable: $t(n) < \left( p(n + 1) - p(n) \right) /{2 \cos \alpha_\text{max}}$
\end{itemize}
